Multiresolution Neural Field Estimation

### 2011-03-01 Multiresolution_framework/ltx/manuscript.tex
removed email addresses from everyone expect Parham

\author{In no particular order: \parham{P. Aram}, \mike{M. Dewar}, \dean{D.R. Freestone,~\IEEEmembership{Graduate Student Member,~IEEE,}}, \ken{K.Scerri}, D.B. Grayden,~\IEEEmembership{Member,~IEEE,} and V. Kadirkamanathan~\IEEEmembership{Member,~IEEE} % <-this % stops a space
\thanks{P. Aram* and V. Kadirkamanathan are with the Department of Automatic Control and Systems Engineering, University of Sheffield, Sheffield, S1 3JD, U.K. (e-mail:p.aram@sheffield.ac.uk; visakan@sheffield.ac.uk).}% <-this % stops a space
\thanks{D.\ R.\ Freestone and D.\ B.\ Grayden are with the Department
of Electrical and Electronic Engineering, The University of Melbourne, and The Bionic Ear Institute, VIC, Australia, (e-mail: dfreestone@bionicear.org; grayden@unimelb.edu.au)}
\thanks{M. Dewar is with the Department of Applied Physics and Applied Mathematics, Columbia University, New York, NY, USA (e-mail:mike.dewar@columbia.edu)}
\thanks{K. Scerri is with the Department of Systems and Control Engineering, University
of Malta, Msida, MSD 2080, Malta (e-mail: kenneth.scerri@um.edu.mt).}}
% <-this % stops a space
%\thanks{Manuscript received April 19, 2005; revised January 11, 2007.}}

>>>>

\author{In no particular order: \parham{P. Aram}, \mike{M. Dewar}, \dean{D.R. Freestone,~\IEEEmembership{Graduate Student Member,~IEEE,}}, \ken{K.Scerri}, D.B. Grayden,~\IEEEmembership{Member,~IEEE,} and V. Kadirkamanathan~\IEEEmembership{Member,~IEEE} % <-this % stops a space
\thanks{P. Aram* and V. Kadirkamanathan are with the Department of Automatic Control and Systems Engineering, University of Sheffield, Sheffield, S1 3JD, U.K. (e-mail:p.aram@sheffield.ac.uk; visakan@sheffield.ac.uk).}% <-this % stops a space
\thanks{D.\ R.\ Freestone and D.\ B.\ Grayden are with the Department
of Electrical and Electronic Engineering, The University of Melbourne, and The Bionic Ear Institute, VIC, Australia}
\thanks{M. Dewar is with the Department of Applied Physics and Applied Mathematics, Columbia University, New York, NY, USA}
\thanks{K. Scerri is with the Department of Systems and Control Engineering, University
of Malta, Msida, MSD 2080, Malta.}}
% <-this % stops a space
%\thanks{Manuscript received April 19, 2005; revised January 11, 2007.}}
